### 2021-05-03 paper/preprint/paper_revised_submission_april2021_apa.Rmd
new .rmd integrating analyses and revamped data frames

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

@@

```{r}
## Read in data 
load(here::here('data/data_preprint/all_vid_data_from_bbs_june2020.RData')) # all detections
load(here::here('data/data_preprint/all_centered_vid_data_from_bbs_june2020.RData')) # centered cropped
```

```{r}
load(here::here('data/data_preprint/gold_sample_from_bbs_june2020.RData')) # gold sample detections
load(here::here('data/data_preprint/gold_sample_annotations2020-01-31.RData')) # human annotations
```

```{r} 
### How large is the dataset we're analyzing?
num_frames = sum(all_vid_data$num_detect)

fps=30
num_seconds = sum(all_vid_data$num_detect)/fps
num_videos = length(unique(all_vid_data$vid_name))
num_minutes = num_seconds/60
num_hours = num_minutes/60
num_days = num_hours/24

@@

## Dataset
The dataset is described in detail in @SAYcam; we summarize these details here. Children wore Veho Muvi miniature cameras mounted on a custom camping headlamp harness ("headcams") at least twice weekly, for approximately one hour per recording session. One weekly session was on the same day each week at a roughly constant time of day, while the other(s) were chosen arbitrarily at the participating family’s discretion. At the time of the recording, all three children were in single-child households.  Videos captured by the headcam were 640x480 pixels, and a fisheye lens was attached to the camera to increase the field of view to approximately 109 degrees horizontal x 70 degrees vertical. Videos ^[All videos are available at https://nyu.databrary.org/volume/564 ] with technical errors or that were not taken from the egocentric perspective were excluded from the dataset. While data collection for the third child (Y) is still ongoing, here we analyze `r num_videos` videos, with a total duration of `r round(num_hours,2)` hours (>40 million frames).

```{r examples, include = T, fig.env = "figure*", fig.pos = "h", fig.align='center', fig.width=8, fig.height=3.5, set.cap.width=T, num.cols.cap=2, fig.align = "center", fig.cap = "Example frames taken from the dataset, illustrating variability in the infant perspective across different locations. OpenPose detections are shown overlaid on these images (green dots = face, red dots = hands, orange dots = pose)."}
examples <- png::readPNG("figs/modifiedOPfigure_v4.png")
grid::grid.raster(examples)
```

@@

 ## output prfs
 face_performance = return_prf_short(gold_sample$face_eval_ketan)
 hand_performance = return_prf_short(gold_sample$hand_eval_ketan)
```

```{r}
### Examine gold sample performance by child hands
load(here::here('data/data_preprint/child_adult_hand_annotations_by_frame.RData'))
# 
hands_missed <- gold_sample %>%
  left_join(child_adult_hand_annotations, by=(c("vid_name","frame"))) %>%
  filter(!is.na(full_image_path)) %>%
  filter(hand_eval_ketan == 'FN')

@@

```{r} 
### Load turk hand annotations with all bounding boxes (multiple dets per frame)
load(here::here('data/data_preprint/hand_annotations_2020-01-29.RData'))

@@

To test the validity of OpenPose's hand and face detections, we compared the accuracy of these detections relative to human annotations of 24,000 frames selected uniformly at random from videos of two children (S and A). Frames were jointly annotated for the presence of faces and hands by one author. A second set of coders recruited via AMT (Amazon Mechanical Turk) additionally annotated 3150 frames; agreement with the primary coder was >95%.

@@

To evaluate OpenPose's performance, we compared its detections to the manually-annotated gold set of frames, calculating precision (hits / hits + false alarms), recall (hits / hits + misses), and F-score (the harmonic mean of precision and recall).  In our data, for faces, the F-score was `r round(face_performance[3],2)`, with a precision of `r round(face_performance[1],2)` and recall of `r round(face_performance[2],2)`. For hands, the F-score was `r round(hand_performance[3],2)`, with a precision of `r round(hand_performance[1],2)` and recall of `r round(hand_performance[2],2)`. While face and hand detections showed moderately good precision, face detections were overall slightly more accurate than hand detections.  In general, hand detections suffered from fairly low recall, indicating that OpenPose likely underestimated the proportion of hands in the dataset.

@@

```{r}
## summary for all detections
summary_by_age <- all_vid_data %>%
  filter(!is.na(age_days)) %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
  group_by(age_day_bin, child_id) %>%
  summarize(num_frames_total = sum(num_detect), num_faces = sum(num_faces), num_hands = sum(num_hands), prop_faces_summary = num_faces / num_frames_total, prop_hands_summary = num_hands / num_frames_total)
```

```{r}
## summary for centered detections
summary_by_age_center <- all_vid_data_center %>%
  filter(!is.na(age_days)) %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
  group_by(age_day_bin, child_id) %>%
  summarize(num_frames_total = sum(num_frames), num_faces = sum(num_faces), num_hands = sum(num_hands), prop_faces_summary = num_faces / num_frames_total, prop_hands_summary = num_hands / num_frames_total)
```

```{R}
#### Make wide format for plotting
wide_uncropped <- summary_by_age %>%
  gather(region, prop, prop_faces_summary, prop_hands_summary) %>%
  mutate(approach = "uncropped",
         region = ifelse(region == "prop_faces_summary","Face","Hands"))  %>%
  filter(num_frames_total > 5000) # eliminate small data point that skews scaling

wide_center <- summary_by_age_center %>%
  gather(region, prop, prop_faces_summary, prop_hands_summary) %>%
  mutate(approach = "centered",
         region = ifelse(region == "prop_faces_summary","Face","Hands"))  %>%
  filter(num_frames_total > 5000) # eliminate small data point that skews scaling 
```

```{r FacesAndHands, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of faces and hands seen as a function of age for each child in the dataset. Data are binned by each week that the videos were filmed and scaled by the number of frames in that age range. Dashed lines show estimated trend lines from proportion of faces/hands in view when detections are restricted to the center FOV, reducing the contribution of children's own hands."}

ggplot(wide_uncropped, 
       aes(x=age_day_bin, y=prop, 
           size=log10(num_frames_total),
           col=region)) +
  geom_point(alpha=.2) +
  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = FALSE) + # geom_smooth(show.legend = FALSE) or move these below legend?
  geom_smooth(data = wide_center, span=10, aes(weight = num_frames_total), show.legend = FALSE, 
              lty = 2, span=10, se = FALSE) +
  ylab('Proportion Detections') + 
  xlab('Age (Months)') +
  ylim(0,.5) +
  facet_grid(.~child_id) + 
  theme_few(base_size=9) +
  ggthemes::scale_color_solarized(name = "") + 
  scale_size_continuous(name = "Detections (Log 10)") +
  theme(legend.text=element_text(size=8)) +
  theme(legend.position="bottom")

@@

@@

However, the most striking result from these analyses is a much overall greater proportion of hands in view than have previously been reported [@Fausey2016]. We found this to be true across all ages, in all three children, and regardless of whether we analyzed human annotations (on the 24K random subset, see dotted lines in Figure \ref{fig:FacesAndHands}) or OpenPose annotations on the entire dataset (see solid lines in Figure \ref{fig:FacesAndHands}). This is notable especially given that OpenPose showed relatively low recall for hands, indicating that this may be an underestimate of the proportion of hands in view. Nonetheless, one reason this could be the case is the much larger field of view that was captured by the cameras used in this study: These cameras were outfitted with a fish-eye lens in an attempt to capture as much of the children’s field of view as possible, leading to a larger field of view (109 degrees horizontal x 70 degrees vertical) than in many previous studies; for example, in @Fausey2016 the FOV was 69 x 41 degrees. This larger FOV may have allowed the SAYCam cameras to capture not only the presence of a social partner’s hands interacting with objects or gestures, but also the children’s own hands, leading to more frequent hand detections.

As children's hands tended to occur in the lower visual field (see Figure \ref{fig:handLocation}), we thus re-analyzed the entire dataset while restricting our analysis to the center field of view, decreasing the proportion of hand detections from `r round(sum(all_vid_data$num_hands)/sum(all_vid_data$num_detect),2)*100`% to `r round(sum(all_vid_data_center$num_hands)/sum(all_vid_data_center$num_frames),2)*100`%, but only decreased face detections from `r round(sum(all_vid_data$num_faces)/sum(all_vid_data$num_detect),2)*100`% to `r round(sum(all_vid_data_center$num_faces)/sum(all_vid_data_center$num_frames),3)*100`%. This cropping likely removed both the majority of detections of children's own hands but also some detections of adult hands (see Figure \ref{fig:handLocation}), especially as OpenPose was biased to miss children's hands when they were in view. Nonetheless, within this modified field of view, we still observed more hand detections than face detections (see dashed lines in Figure \ref{fig:FacesAndHands}).

```{r eval=FALSE}
summary_by_age_days_centered <- all_vid_data_center %>%
  group_by(age_days,child_id) %>%
  summarize(num_faces = sum(num_faces), num_hands = sum(num_hands), num_detect = sum(num_frames)) %>%
  mutate(prop_faces = num_faces / num_detect, prop_hands = num_hands / num_detect) 
summary_by_age_days_centered$age_scale <- scale(summary_by_age_days_centered$age_days, scale = FALSE)[,1] / 30.3

summary_by_age_days <- all_vid_data %>%
  group_by(age_days,child_id) %>%
  summarize(num_faces = sum(num_faces), num_hands = sum(num_hands), num_detect = sum(num_frames)) %>%
  mutate(prop_faces = num_faces / num_detect, prop_hands = num_hands / num_detect) 
summary_by_age_days$age_scale <- scale(summary_by_age_days$age_days, scale = FALSE)[,1] / 30.3

@@

```{r eval=FALSE}
# run lmer models -- faces over age
faces_model_full_age_out = summary(lmer(prop_faces ~ age_scale + (1 | child_id), data = summary_by_age_days_centered))

# hands over age
hands_model_full_age_out = summary(lmer(prop_hands ~ age_scale + (1 | child_id), data = summary_by_age_days_centered))

# explicit modeling of faces vs. hands and interaction with age
# main effect of ages and regions; no interaction.
wide_centered_age_days <- summary_by_age_days_centered %>%
  gather(region, prop, prop_faces, prop_hands) %>%
  mutate(approach = "cropped",
         region = ifelse(region == "prop_faces","Face","Hands"))

diff_model_full_age_out = summary(lmer(prop ~ region*age_scale + (1 | child_id), data = wide_centered_age_days))
```

@@

\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & Estimate & Std. Error & df & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept) & 0.100 & 0.014 & 1.955 & 7.049 & 0.021 \\ 
  Age  & -0.002 & 0.001 & 386.972 & -4.461 & 0.000 \\ 
   \hline
\end{tabular}
\caption{Model coefficients from a linear mixed model predicting the proportion of faces seen by infants in the center FOV.} 
\end{table}

\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & Estimate & Std. Error & df & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept) & 0.166 & 0.011 & 2.082 & 15.340 & 0.004 \\ 
  Age & -0.002 & 0.001 & 380.308 & -3.114 & 0.002 \\ 
   \hline
\end{tabular}
\caption{Model coefficients from a linear mixed model predicting the proportion of hands seen by infants in the center FOV.} 
\end{table}

@@

num_videos_annotated = sum(!is.na(meta$Location))
videos_included = sum(!is.na(meta$Location) & meta$count_locations==1)

# percentage_of_dataset = sum(faces_vs_hands_to_plot$num_detect)/length(d_all$frame)
# num_frames = sum(faces_by_location_to_plot$num_detect)
```

```{r}
vid_data_by_location <- all_vid_data %>%
  mutate(num_frames = num_detect) %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
  left_join(meta) %>%
  filter(!is.na(Location)) %>%
  filter(count_locations==1)

vid_data_centered_by_location <- all_vid_data_center %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
  left_join(meta) %>%
  filter(!is.na(Location)) %>%
  filter(count_locations==1)

# 
vid_data_by_location$Location = droplevels(vid_data_by_location$Location) 
vid_data_centered_by_location$Location = droplevels(vid_data_centered_by_location$Location) # get rid of unused levels (more than 1 location)

# merge locations that seem similar
levels_to_modify = levels(vid_data_by_location$Location)
levels_to_modify = levels(vid_data_centered_by_location$Location)
levels_to_modify[10] = 'Outside' # Outside on property
levels_to_modify[12] = 'Outside' # Off Property

# reset levels for both cropped/uncropped
levels(vid_data_centered_by_location$Location) <- levels_to_modify
levels(vid_data_by_location$Location) <- levels_to_modify

@@

```{r}
face_hand_by_location_centered<- vid_data_centered_by_location %>%
  group_by(Location,child_id,age_day_bin) %>%
  summarize(prop_faces = sum(num_faces)/sum(num_frames), prop_hands = sum(num_hands)/sum(num_frames), num_detect = sum(num_frames))  %>%
  group_by(Location) %>%
  filter(num_detect >12000)

face_hand_by_location <- vid_data_by_location %>%
  group_by(Location,child_id,age_day_bin) %>%
  summarize(prop_faces = sum(num_faces)/sum(num_frames), prop_hands = sum(num_hands)/sum(num_frames), num_detect = sum(num_frames))  %>%
  group_by(Location) %>%
  filter(num_detect >12000)

>>>>

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
                      include:
                        after_body: appendix.tex
---

@@

```{r}
## Read in data 
load(here::here('data/preprocessed_data_2021/all_vid_data_from_bbs_all_detections.RData')) # all detections
```

```{r}
# load(here::here('data/preprocessed_data_2021/gold_sample_from_bbs_2021.RData')) # gold sample detections
load(here::here('data/preprocessed_data_2021/gold_sample_annotations2020-01-31.RData')) # human annotations

load(here::here('data/preprocessed_data_2021/gold_sample_from_bbs_2021_all_detections.RData'))

# all_gold_sample_frames_op_hc = load(here::here('data/preprocessed_data_2021/gold_sample_from_bbs_2021_high_conf_detections.RData')) 
```

```{r} 
### How large is the dataset we're analyzing?
num_frames = sum(all_vid_data$num_frames)

fps=30
num_seconds = sum(all_vid_data$num_frames)/fps
num_videos = length(unique(all_vid_data$vid_name))
num_minutes = num_seconds/60
num_hours = num_minutes/60
num_days = num_hours/24

@@

## Dataset
The dataset is described in detail in @SAYcam; we summarize these details here. Children wore Veho Muvi miniature cameras mounted on a custom camping headlamp harness ("headcams") at least twice weekly, for approximately one hour per recording session. One weekly session was on the same day each week at a roughly constant time of day, while the other(s) were chosen arbitrarily at the participating family’s discretion. At the time of the recording, all three children were in single-child households.  Videos captured by the headcam were 640x480 pixels, and a fisheye lens was attached to the camera to increase the field of view to approximately 109 degrees horizontal x 70 degrees vertical. Videos ^[All videos are available at https://nyu.databrary.org/volume/564 ] with technical errors or that were not taken from the egocentric perspective were excluded from the dataset.  We analyze `r num_videos` videos, with a total duration of `r round(num_hours,2)` hours (>50 million frames).

```{r examples, include = T, fig.env = "figure*", fig.pos = "h", fig.align='center', fig.width=8, fig.height=3.5, set.cap.width=T, num.cols.cap=2,  fig.fullwidth = TRUE, fig.align = "center", fig.cap = "Example frames taken from the dataset, illustrating variability in the infant perspective across different locations. OpenPose detections are shown overlaid on these images (green dots = face, red dots = hands, orange dots = pose)."}
examples <- png::readPNG("figs/modifiedOPfigure_v4.png")
grid::grid.raster(examples)
```

@@

 ## output prfs
 face_performance = return_prf_short(gold_sample$face_eval_ketan)
 hand_performance = return_prf_short(gold_sample$hand_eval_ketan)

```{r}
## for high confidence detections
gold_sample_hc <- gold_sample %>%
  select(vid_name, frame, face_present_ketan, hand_present_ketan) %>%
  mutate(face_present_ketan = as.logical(face_present_ketan), hand_present_ketan = as.logical(hand_present_ketan)) %>%
  right_join(all_gold_sample_frames_op_hc) %>% # HIGH CONF DF
  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected))

face_performance_hc = return_prf_short(gold_sample_hc$face_eval_ketan)
hand_performance_hc = return_prf_short(gold_sample_hc$hand_eval_ketan)
```

```{r}
### Examine gold sample performance by child hands
load(here::here('data/preprocessed_data_2021/child_adult_hand_annotations_by_frame.RData'))
# 
hands_missed <- gold_sample %>%
  left_join(child_adult_hand_annotations, by=(c("vid_name","frame"))) %>%
  filter(!is.na(full_image_path)) %>%
  filter(hand_eval_ketan == 'FN')

@@

```{r} 
### Load turk hand annotations with all bounding boxes (multiple dets per frame)
load(here::here('data/preprocessed_data_2021/hand_annotations_2020-01-29.RData'))

@@

To test the validity of OpenPose's hand and face detections, we compared the accuracy of these detections relative to human annotations of 24,000 frames selected uniformly at random from videos of two children (S and A); XX frames with allocentric videos were excluded, as were these videos from the rest of analyses. Frames were jointly annotated for the presence of faces and hands by one author. A second set of coders recruited via AMT (Amazon Mechanical Turk) additionally annotated 3150 frames; agreement with the primary coder was >95%.

@@

To evaluate OpenPose's performance, we compared its detections to the manually-annotated gold set of frames, calculating precision (hits / hits + false alarms), recall (hits / hits + misses), and F-score (the harmonic mean of precision and recall).  In our data, for faces, the F-score was `r round(face_performance[3],2)`, with a precision of `r round(face_performance[1],2)` and recall of `r round(face_performance[2],2)`. For hands, the F-score was `r round(hand_performance[3],2)`, with a precision of `r round(hand_performance[1],2)` and recall of `r round(hand_performance[2],2)`. While face and hand detections showed moderately good precision, face detections were overall slightly more accurate than hand detections.  In general, hand detections suffered from fairly low recall, indicating that OpenPose likely underestimated the proportion of hands in the dataset. 
We also evaluated OpenPose's performance while restricting detections to high-confidence detections (>.5 confidence, default threshold for visualization). For faces, we found that the F-score was `r round(face_performance_hc[3],2)`, with a precision of `r round(face_performance_hc[1],2)` and recall of `r round(face_performance_hc[2],2)`. For hands, the F-score for high confidence detections `r round(hand_performance_hc[3],2)`, with a precision of `r round(hand_performance_hc[1],2)` and recall of `r round(hand_performance_hc[2],2)`. Thus, as in prior work [@long2020automated], while precision was much highe for both faces and hands, the lower recall for high-confidence detection indicates that these lower-confidence detections still index the presence of social information in the infant view.

@@

```{r}
## summary for all detections
face_hand_by_age <- all_vid_data %>%
  ungroup() %>%
  tidyr::replace_na(list(faces_and_hands=0)) %>%
  group_by(age_day_bin, child_id) %>%
  summarize(num_frames_total = sum(num_frames), 
            # prop faces overall
            num_faces = sum(num_faces), 
            num_hands = sum(num_hands), 
            prop_faces = num_faces / num_frames_total, 
            prop_hands = num_hands / num_frames_total,
            # in center FOV
            num_faces_center = sum(num_faces_center, na.rm=TRUE), 
            num_hands_center = sum(num_hands_center, na.rm=TRUE), 
            prop_faces_center = num_faces_center / num_frames_total, 
            prop_hands_center = num_hands_center / num_frames_total,
            # detailed face info
            prop_full_faces = sum(num_full_faces, na.rm=TRUE)/num_frames_total,
            prop_faces_and_hands = sum(faces_and_hands)/num_frames_total,
            # face/hand contingency
            prop_faces_with_hands = sum(faces_and_hands, na.rm=TRUE)/num_faces, 
            prop_hands_with_faces = sum(faces_and_hands, na.rm=TRUE)/num_hands 
            )

@@

```{R}
#### Make longer format for plotting
all_detections <- face_hand_by_age %>%
  filter(num_frames_total > 2000) %>% # eliminate small data point that skews scaling
  select(prop_faces, prop_hands, num_frames_total, age_day_bin, child_id) %>%
  pivot_longer(cols = c(prop_faces, prop_hands), names_to = "region", values_to = "prop") %>%
  mutate(approach = "uncropped",
         region = ifelse(region == "prop_faces","Faces","Hands"))

centered <- face_hand_by_age %>%
  filter(num_frames_total > 2000) %>% # eliminate small data point that skews scaling
  select(prop_faces_center, prop_hands_center, num_frames_total, age_day_bin, child_id) %>%
  gather(region, prop, prop_faces_center, prop_hands_center) %>%
  mutate(approach = "centered",
         region = ifelse(region == "prop_faces_center","Faces","Hands"))
```

```{r FacesAndHands, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of faces and hands seen as a function of age for each child in the dataset. Data are binned by each week that the videos were filmed and scaled by the number of frames in that age range. Dashed lines show estimated trend lines from proportion of faces/hands in view when detections are restricted to the center FOV, reducing the contribution of children's own hands."}
ggplot(all_detections, 
       aes(x=age_day_bin, y=prop, 
           size=log10(num_frames_total),
           col=region)) +
  geom_point(alpha=.2) +
  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = FALSE) + 
  geom_smooth(data = centered, span=10, aes(weight = num_frames_total), show.legend = TRUE,
              lty = 2, span=10, se = FALSE) +
  ylab('Proportion Detections') + 
  xlab('Age (Months)') +
  ylim(0,.5) +
  facet_grid(.~child_id) + 
  theme_few(base_size=9) +
  ggthemes::scale_color_solarized(name = "") + 
  theme(legend.text=element_text(size=8)) +
  guides(size = FALSE) +
  theme(legend.position="bottom") 
```

@@

However, the most striking result from these analyses is a much overall greater proportion of hands in view than have previously been reported [@Fausey2016]. We found this to be true across all ages, in all three children, and regardless of whether we analyzed human annotations (on the 24K random subset, see dotted lines in Appendix Figure \ref{fig:goldSetSanity}) or OpenPose annotations on the entire dataset (see solid lines in Figure \ref{fig:FacesAndHands}). This is notable especially given that OpenPose showed relatively low recall for hands, indicating that this may be an underestimate of the proportion of hands in view. Nonetheless, one reason this could be the case is the much larger field of view that was captured by the cameras used in this study: These cameras were outfitted with a fish-eye lens in an attempt to capture as much of the children’s field of view as possible, leading to a larger field of view (109 degrees horizontal x 70 degrees vertical) than in many previous studies; for example, in @Fausey2016 the FOV was 69 x 41 degrees. This larger FOV may have allowed the SAYCam cameras to capture not only the presence of a social partner’s hands interacting with objects or gestures, but also the children’s own hands, leading to more frequent hand detections.

As children's hands tended to occur in the lower visual field (see Figure \ref{fig:handLocation}), we thus re-analyzed the entire dataset while restricting our analysis to the center field of view, decreasing the proportion of hand detections from `r round(sum(all_vid_data$num_hands)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_hands_center)/sum(all_vid_data$num_frames),2)*100`%, but only decreased face detections from `r round(sum(all_vid_data$num_faces)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_faces_center)/sum(all_vid_data$num_frames),3)*100`%. This cropping likely removed both the majority of detections of children's own hands but also some detections of adult hands (see Figure \ref{fig:handLocation}), especially as OpenPose was biased to miss children's hands when they were in view. Nonetheless, within this modified field of view, we still observed more hand detections than face detections (see dashed lines in Figure \ref{fig:FacesAndHands}).

In a second set of analysis, we explored finer-grained changes in the ways in which infants’ experienced this social information across development, capitalizing on the fact that OpenPose provides not only face and hand detections but also positional keypoints. In particular, we explored this dataset with the idea that younger children may tend to see larger, complete faces towards the center of their visual field—that is, that have both eyes, nose, and a mouth in view—while older children may experience more incomplete views of faces.

First, we explored the proportion of faces that were detected that tended to be “complete” faces—that is, faces where the eyes, mouth, and nose were all detected by OpenPose. Figure \ref{eye_distance} shows that roughly half of the faces detected by OpenPose were full-view faces, suggesting that infants’ are often seeing partial views of their caregiver’s faces. More generally, we found that the proportion of full faces in view roughly followed the proportion of faces in view, again converging with the findings of Fausey et al., 2016 showing a decrease in the proportion of faces in the infant view across early development.

```{r}
face_hand_detailed_plot <- face_hand_by_age %>%
  gather(region, prop, prop_full_faces, prop_faces, prop_hands, prop_faces_and_hands) %>%
  mutate(approach = "uncropped",
         region = case_when(region == "prop_faces" ~"All faces",
                            region == "prop_full_faces" ~ "Full faces (eyes, nose, mouth visible)",
                            region == "prop_hands" ~ "All hands",
                            region == "prop_faces_and_hands" ~ "Both hands and faces visible"),
         child_name = case_when(child_id =='A' ~ "Child A",
                      child_id == "S" ~ "Child S",
                      child_id == "Y" ~ "Child Y")) %>%
  filter(num_frames_total > 5000) # skews scaling of detections to have this 1 sparse age bin

@@

```{r faceHandDetailed, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Proportion of face, hand, 'full' face (i.e. nose, mouth, and nose visilbe), and joint face/hand detections as a function of age for each child in the dataset. Data are binned by each week that the videos were filmed and scaled by the number of frames in that age range. }
ggplot(face_hand_detailed_plot, 
       aes(x=age_day_bin, y=prop, 
           col=region)) +
  geom_point(alpha=.1, aes(size=log10(num_frames_total)), show.legend= FALSE) +
  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = TRUE) + 
  ylab('Proportion Detections') + 
  xlab('Age (Months)') +
  ylim(0,.5) +
  facet_grid(.~child_name) + 
  theme_few(base_size=12) +
  scale_color_manual(values = c( "#2048d6","#d62020","#751098","#142c83"), name = "") +
  scale_size_continuous(name = "") +
  guides(size = FALSE) +
  theme(legend.text=element_text(size=8)) +
  theme(legend.position="bottom") 
```

```{r}
# eye distance... ugh
eye_dist <- all_vid_data %>%
  group_by(child_id, age_day_bin) %>%
  summarize(eye_distance = mean(avg_eye_distance, na.rm=TRUE), num_frames_total = sum(num_frames)) %>%
  filter(num_frames>2000)
```

```{r avgEyeDistance, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=3, fig.height=3, fig.cap = "Average distance between eyes in faces detected as a function of age for each child in the dataset (each color = different child). Data are binned by each week that the videos were filmed and scaled by the number of frames in that age range. }
ggplot(eye_dist, 
       aes(x=age_day_bin, y=eye_distance, 
           col=child_id)) +
  geom_point(alpha=.1, aes(size=log10(num_frames_total)), show.legend= FALSE) +
  geom_smooth(method='lm', aes(weight = num_frames_total), show.legend = TRUE) + 
  ylab('Average distance between eyes') + 
  xlab('Age (Months)') +
  theme_few(base_size=12) +
  scale_color_brewer(palette="Dark2") +
  guides(size = FALSE) +
  theme(legend.text=element_text(size=12)) +
  theme(legend.position="none", aspect.ratio=.75) 
```

```{r}
# eye distance... ugh
face_hand_contingency <- face_hand_by_age %>%
  pivot_longer(c(prop_faces_with_hands, prop_hands_with_faces), values_to="prop", names_to = "region") %>%
  mutate(region = case_when(
    region == "prop_faces_with_hands" ~ "Proportion hands (given face detection)",
    region == "prop_hands_with_faces" ~ "Proportion faces (given hand detection)"))
```

```{r faceHandContingency, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=5, fig.height=3, fig.cap = "Face hand contingnecy }
ggplot(face_hand_contingency, 
       aes(x=age_day_bin, y=prop, 
           col=child_id)) +
  geom_point(alpha=.1, aes(size=log10(num_frames_total)), show.legend= FALSE) +
  geom_smooth(method='lm', aes(weight = num_frames_total), show.legend = TRUE) + 
  ylab('Average distance between eyes') + 
  xlab('Age (Months)') +
  theme_few(base_size=12) +
  facet_grid(~region) +
  scale_color_brewer(palette="Dark2") +
  guides(size = FALSE) +
  theme(legend.text=element_text(size=12)) +
  theme(legend.position="none", aspect.ratio=.75) 
```

In addition, we found faces tended to be farther away from children across age (restricting our analysis to faces where both eyes were detected). Figure X shows the average interpupillary distance on faces as a function of each child’s age at the time of recording, showing a trend from larger, closer faces (with a larger interpupillary distance) to smaller faces that were farther away (with a smaller interpupillary distance). We saw relatively similar trends across all three children in the dataset, and a linear mixed-effect model confirmed a main effect of age (STATS; see repository for full model specification). However, when we examined the size of all faces and hands in the infant view, we found consistency across development (see Appendix, Figure X): while faces (and full body poses) were of course bigger than hands on average, these properties were relatively stable across development and children (see Appendix, Figure X).

Next, we explored where in the visual field children tended to see faces and hands, suspecting, perhaps, that these distributions might become wider as children grow older and learn to locomote on their own, following preliminary analyses from Frank, 2012.  As expected, faces tended to appear in the upper visual field vs. hands, which tended to be more centrally located. Figure XX shows the average position of faces and hands in the visual field; each dot represents the average position from one video within a given age range. However, we found little evidence for any changes in the positions of faces and hands across age, suggesting that this is a relatively stable property of infants’ -- and likely adults’ -- visual environment from 6 months of age.

```{r eval=FALSE}
summary_by_age_days <- all_vid_data %>%
  group_by(age_days,child_id) %>%
  summarize(num_faces = sum(num_faces), 
            num_faces_center = sum(num_faces_center), 
            num_hands = sum(num_hands), 
            num_hands_center = sum(num_hands_center), 
            num_detect = sum(num_frames)) %>%
  mutate(prop_faces = num_faces / num_detect, 
         prop_hands = num_hands / num_detect,
         prop_faces_center = num_faces_center / num_detect, 
          prop_hands_center = num_hands_center / num_detect)

long_summary_by_age_days <- summary_by_age_days %>%
  select(prop_faces, prop_hands, age_days, child_id) %>%
  pivot_longer(col = c(prop_faces, prop_hands), names_to="region", values_to = "prop")

summary_by_age_days$age_scale <- scale(summary_by_age_days$age_days, scale = FALSE)[,1] / 30.3
long_summary_by_age_days$age_scale <- scale(long_summary_by_age_days$age_days, scale = FALSE)[,1] / 30.3

```{r eval=FALSE}
# run lmer models -- faces over age
faces_model_full_age_out = summary(lmer(prop_faces_center ~ age_scale + (1 | child_id), data = summary_by_age_days))

# hands over age
hands_model_full_age_out = summary(lmer(prop_hands_center ~ age_scale + (1 | child_id), data = summary_by_age_days))

# explicit modeling of faces vs. hands and interaction with age
# main effect of ages and regions; no interaction.
diff_model_full_age_out = summary(lmer(prop ~ region*age_scale + (1 | child_id), data = long_summary_by_age_days))
```

@@

\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & Estimate & Std. Error & df & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept)  9.845e-02  1.049e-02  1.956e+00   9.386  0.01198 * 
Age   -1.418e-03  4.503e-04  4.310e+02  -3.150  0.00175 **
   \hline
\end{tabular}
\caption{Model coefficients from a linear mixed model predicting the proportion of faces seen by infants in the center FOV.} 
\end{table}

\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & Estimate & Std. Error & df & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept)  1.612e-01  8.930e-03  1.881e+00   18.05   0.0040 **
Age   -9.987e-04  5.945e-04  4.287e+02   -1.68   0.0937 
   \hline
\end{tabular}
\caption{Model coefficients from a linear mixed model predicting the proportion of hands seen by infants in the center FOV.} 
\end{table}

@@

num_videos_annotated = sum(!is.na(meta$Location))
videos_included = sum(!is.na(meta$Location) & meta$count_locations==1)
```

```{r}
vid_data_by_location <- all_vid_data %>%
  left_join(meta) %>%
  filter(!is.na(Location)) %>%
  filter(count_locations==1) 
# 
vid_data_by_location$Location = droplevels(vid_data_by_location$Location)

# merge locations that seem similar
levels_to_modify = levels(vid_data_by_location$Location)
levels_to_modify[10] = 'Outside' # Outside on property
levels_to_modify[12] = 'Outside' # Off Property

# reset levels for both cropped/uncropped
levels(vid_data_by_location$Location) <- levels_to_modify

percentage_of_dataset = sum(vid_data_by_location$num_frames)/sum(all_vid_data$num_frames)
num_frames = sum(vid_data_by_location$num_frames)

@@

```{r}
face_hand_by_location <- vid_data_by_location %>%
  group_by(Location,child_id,age_day_bin) %>%
  summarize(num_detect = sum(num_frames),prop_faces = sum(num_faces)/num_detect, prop_hands = sum(num_hands)/num_detect,  prop_hands_center =  sum(num_hands_center, na.rm=TRUE)/num_detect, prop_faces_center = sum(num_faces_center, na.rm=TRUE)/num_detect)  %>%
  group_by(Location) %>%
  filter(num_detect > 2000)

## Compute CIs for faces/hands by each location, and then merge back raw data so they can be plotted together
## Get rid of any locations where we didn't have enough data to make a CI (not more than 1 age_bin)
hands_to_plot_centered <- face_hand_by_location %>%
  group_by(Location, child_id) %>%
  multi_boot_standard(col="prop_hands_center") %>%
  mutate(region = "Hands (Center)") %>%
  ungroup %>%
  left_join(face_hand_by_location) %>%
  mutate(prop = prop_hands_center) %>%
  filter(!is.na(ci_lower))

faces_to_plot_centered <- face_hand_by_location %>%
  group_by(Location, child_id) %>%
  multi_boot_standard(col="prop_faces_center") %>%
  mutate(region = "Face (Center)") %>%
  ungroup %>%
  left_join(face_hand_by_location) %>%
  mutate(prop = prop_faces_center) %>%
  filter(!is.na(ci_lower))  # if we didn't have enough points to make a CI, filter
